---
title: "Quantitive Management Modelling -Assignment 3 : Shadow Price , Reduced Cost"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### 1. Importing Library
```{r}
# Importing "lpSolveAPI" library
library(lpSolveAPI)
```
### 2. Assigning Constraints and decision Variables
```{r}
# 1.Assigning number of constraints and decision variables
lprec <- make.lp(0, 9)

```

### 3. Setting up Objective function ,Constraints , decision variables

```{r}

# 3.1 Objective Function
set.objfn(lprec, c(420, 360, 300, 420, 360, 300, 420, 360, 300))
lp.control(lprec,sense='max') # setting it to maximize(default is minimize)

# 3.2 Providing values for each constraint

add.constraint(lprec, c(1, 1, 1), "<=", 750,indices =c(1,2,3) )
add.constraint(lprec, c(1, 1, 1), "<=", 900 , indices =c(4,5,6) )
add.constraint(lprec, c(1, 1, 1), "<=", 450,indices=c(7,8,9))
add.constraint(lprec, c(20, 15, 12), "<=", 13000,indices =c(1,2,3) )
add.constraint(lprec, c(20, 15, 12), "<=", 12000,indices = c(4,5,6))
add.constraint(lprec, c(20, 15, 12), "<=", 5000 , indices = c(7,8,9))
add.constraint(lprec, c(1, 1, 1), "<=", 900, indices=c(1,2,3))
add.constraint(lprec, c(1, 1, 1), "<=", 1200,indices = c(4,5,6))
add.constraint(lprec, c(1, 1, 1), "<=", 750, indices = c(7,8,9))
add.constraint(lprec, c(900, 900, 900, -750, -750 ,-750), "=", 0,indices = c(1,2,3,4,5,6))
add.constraint(lprec, c(450, 450, 450, -900, -900, -900), "=", 0, indices = c(4,5,6,7,8,9))


# 3.3 Naming the decision variables (column) and constraints (rows)

rownames <- c("Plant1_Production", "Plant2_Production", "Plant3_Production", "Plant1_Storage_Space", "Plant2_Storage_Space", "Plant3_Storage_Space", "Plant1_Sales_Forecast", "Plant2_Sales_Forecast", "Plant3_Sales_Forecast", "Capacity1", "Capacity2")

colnames <- c("Plant1_Large", "Plant1_Medium", "Plant1_Small","Plant2_Large", "Plant2_Medium", "Plant2_Small","Plant3_Large", "Plant3_Medium", "Plant3_Small")

dimnames(lprec) <- list(rownames,colnames)
```
### 4. View the linear program external pointer

```{r}
lprec
```

### 5. Save the LP model into a file
```{r}
write.lp(lprec, filename = "weiglet_Assignment3_Shadow_Reduced_Price.lp", type = "lp")


weiglet <- read.lp("weiglet_Assignment3_Shadow_Reduced_Price.lp") # create an lp object weiglet
```

### 6. Reading from file and solving it
```{r}
solve(weiglet)                   # Solution
get.objective(weiglet)           # get objective value
get.variables(weiglet)           # get values of decision variables
get.constraints(weiglet)         # get constraints

```
### 7. Identifying Shadow price :
```{r}
#options(scipen = 0)
get.sensitivity.rhs(weiglet)  # get shadow prices

```

### 8. Identifying Reduced Cost:

```{r}
get.sensitivity.obj(weiglet)  # get reduced cost
```

### 9. Results:
+ Used **"lpSolveAPI"** library to solve the LP problem.
+ Since, it is an maximization problem  , we have determined the maximized profit.
+ As per the above results:
+ The  maximum total net profit per day,Z= **696000**.
+ **Identified Shadow Price** and **reduced cost**.
+ Also determined the **ranges for shadow price** and **reduced costs** , such that within which the optimum solution will not change.

-----------------------------------------------------------------------------------------------------------------------
-----------------------------------------------------------------------------------------------------------------------

