---
title: "Quantative Management - Assignment-4"
output:
  pdf_document:
    latex_engine: xelatex
  html_document: default
---

**Heart Start produces automated external defibrillators (AEDs) in each of two different plants (A and B). The unit production costs and monthly production capacity of the two plants are indicated in the table below. The AEDs are sold through three wholesalers. The shipping cost from each plant to the warehouse of each wholesaler along with the monthly demand from each wholesaler are also indicated in the table. How many AEDs should be produced in each plant, and how should they be distributed to each of the three wholesaler warehouses so as to minimize the combined cost of production and shipping? **



|Category       |warehouse_1|Warehouse_2|Warehouse_3|Product Cost |Product Capacity
|---------------|--|--|--|-- |--
|Plant A        |22|14|30|600|100
|Plant B        |16|20|24|625|120
|Monthly Deposit|80|60|70



Here we would be applying 2 methods approach:-

1.Using inequalities

2.Using dummy Variables


**Solution 1:Using Inequalities**

Assuming that the plant A is producing X11, X12 & X13 units of AEDs for Warehouse 1, Warehouse 
2 and Warehouse 3 respectively. And plant B is producing X21, X22 & X23 units of AEDs for Warehouse 1, Warehouse 2 and Warehouse 3 respectively. 

So, the total cost will be calculated as sum of Unit Shipping cost to each Warehouse and the Unit production cost: 

𝑍	=	600X11 + 600X12 + 600X13 + 625X21 + 625X22 + 625X23 + 22X11 + 14X12
+ 30X13 + 16X21 + 20X22 + 24X23 
 
Where, Z denotes the total cost.

As mentioned above, plant A has monthly production capacity of 100 AEDS. And plant B has monthly production capacity of 120 AEDs. Therefore, 
 
 X11	+	X12	+	X13	+ X14<=100 
 X21 +  X22 +  X23 <=120  
 
Also, monthly demand for each warehouse is as follows : 
 
X11	+	X21 = 80 
 
X12 + X22 = 60 
 
X13 + X23 = 70 
 
Hence, the Linear programming model should be defined as: 

**The decision variables are:** 
 
      X11 = units of AEDs shipped from Plant A to Warehouse 1  
      X12 = units of AEDs shipped from Plant A to Warehouse 2  
      X13 = units of AEDs shipped from Plant A to Warehouse 3 
      X21 = units of AEDs shipped from Plant B to Warehouse 1 
      X22 = units of AEDs shipped from Plant B to Warehouse 2 
      X23 = units of AEDs shipped from Plant B to Warehouse 3 
 
 **Objective function:**
 
      Minimize   Z = 622X11 + 614X12 + 630X13 + 640X21 + 645X22 + 649X23 
 
	 **subject to :**
	 	 	               X11	+	X12	+	X13	<=100 
	                   X21 +  X22 +  X23 <=120 
	                            X11	+	X21 =	80 
	                            X12	+	X22 =	60 
	                            X13	+	X33 =	70 
	                            X14	+	X24 =	10 

 
 	 	       
	And 	        X11, X12, X13, X21, X22, X23	>=	0 
	

Now, we will solve  this transportation problem using lpsolve in R.Below is the solution based on the above formulations.


```{r}
# Solution 1 using inequalities

# Let us set up the Linear problem. Note that we have 6 decision variables and 5 constraints. 

library(lpSolveAPI)

lprec <- make.lp(5, 6)

# Set the minimization objective function

set.objfn(lprec, c(622, 614, 630, 641, 645, 649))
lp.control(lprec,sense='min')

# Set values for the rows (set the Left hand side constraints)

set.row(lprec, 1, c(1, 1, 1), indices = c(1, 2, 3))
set.row(lprec, 2, c(1, 1, 1), indices = c(4, 5, 6))
set.row(lprec, 3, c(1, 1), indices = c(1, 4))
set.row(lprec, 4, c(1, 1), indices = c(2, 5))
set.row(lprec, 5, c(1, 1), indices = c(3, 6))

# Set the right hand side values

rhs <- c(100, 120, 80, 60, 70)
set.rhs(lprec, rhs)

# Set constraint type and set variable types and bound


set.constr.type(lprec, c("<=", "<=", "=", "=", "="))
set.bounds(lprec, lower = rep(0, 6))

# Finally, name the decision variables (column) and constraints (rows)


lp.rownames <- c("CapacityA", "CapacityB", "DemandW1", "DemandW2", "DemandW3")
lp.colnames <- c("PlantAW1", "PlantAW2", "PlantAW3","PlantBW1", "PlantBW2", "PlantBW3")
dimnames(lprec) <- list(lp.rownames, lp.colnames)

# View the linear problem object to make sure it's correct

lprec

# Save this into a file
write.lp(lprec, filename = "AED_firstSolution.lp", type = "lp")
solve(lprec) # Now, solve the model


# Show the value of objective function, variables, constraints and slack

get.objective(lprec)
get.variables(lprec)
get.constraints(lprec)
get.constraints(lprec) - rhs

```
**Observations:**


1. We were **successfully able to solve** the LP problem using inequalities.

2.The  minimized combined cost of production and shipping is  **132790**.

3.The AED should be produced for each plant based on each of the **3 warehouses are 0,60,40,80,0,30**.for Plant1 warehouse 1,Plant1 warehouse 2,Plant 1 warehouse 3,Plant 2 warehouse 1, Plant2 warehouse 2,Plant2 warehouse 3 respectively.





Now let's take look on the dummy variable approach and its outcome.




### **Solution 2: Using Dummy Variables**

Since, the monthly demand is less than the monthly production capacity. Let’s create dummy Warehouse (Warehouse 4) which can accommodate 10 units. The unit shipping cost to the warehouse 4 is $0 since it is dummy warehouse.  

|Category       |warehouse_1|Warehouse_2|Warehouse_3|Warehouse_4|Product Cost |Product Capacity
|---------------|--|--|--|- |-- |-- |
|Plant A        |22|14|30|0|600|100
|Plant B        |16|20|24|0|625|120
|Monthly Deposit|80|60|70|10
 
So now Assume that the plant A produces X11, X12, X13 and X14 units of AEDs for 
Warehouse 1, Warehouse 2, Warehouse 3 and Warehouse 4 respectively. And plant B produces 
X21, X22, X23 & X24 units of AEDs for Warehouse 1, Warehouse 2, Warehouse 3 & Warehouse 4 respectively.

So, the total cost will be calculated as sum of Unit Shipping cost to each Warehouse and the Unit production cost: 

𝑍	=	600X11 + 600X12 + 600X13 + 625X21 + 625X22 + 625X23 + 22X11 + 14X12  +30X13 + 0X14 + 16X21 + 20X22 + 24X23 + 0X24
  
 
Where, Z denotes the total cost. 
Now, plant A has monthly production capacity of 100 AEDS. And plant B has monthly production capacity of 120 AEDs. Therefore, 
	X11	+	X11	+	X13 + X14 =	100 
	X21	+	X22	+	X23 + X24 =	120 
	
Also, monthly demand for each warehouse is as follows  
 
X11	+	X21 = 80 
 
X12 + X22 = 60 
 
X13 + X23 = 70 
 
X14 + X24 = 10 
 
Hence, the Linear programming model should be defined as: 

The decision variables are: 
 
      X11 = units of AEDs shipped from Plant A to Warehouse 1  
      X12 = units of AEDs shipped from Plant A to Warehouse 2  
      X13 = units of AEDs shipped from Plant A to Warehouse 3 
      X14 = units of AEDs shipped from Plant A to Warehouse 4 
      X21 = units of AEDs shipped from Plant B to Warehouse 1 
      X22 = units of AEDs shipped from Plant B to Warehouse 2 
      X23 = units of AEDs shipped from Plant B to Warehouse 3 
      X24 = units of AEDs shipped from Plant B to Warehouse 4 
 
 
 Minimize   𝑍 = 622X11 + 614X12 + 630X13 + 0X14	+ 640X21 + 645X22 + 649X23 + 0X24 
 
subject to 
	 	 	                        X11	+	X12	+	X13	+ X14	=	100 
	                            X21	+	X22	+	X23	+ X24 =	120 
	                            X11	+	X21 =	80 
	                            X12	+	X22 =	60 
	                            X13	+	X33 =	70 
	                            X14	+	X24 =	10 
 	 	         	
 
 	 	       
	And 	        X11, X12, X13, X14, X21, X22, X23, X24	>=	0 
	
	Now , lets solve the dummy variable solution using lpsolve in R.

```{r}

# Let us set up the Linear problem. Note that we had 8 decision variables and 6 constraints. 

lprec_dummy <- make.lp(6, 8)

# Setting the minimization objective function

set.objfn(lprec_dummy, c(622, 614, 630, 0, 641, 645, 649, 0))
lp.control(lprec_dummy, sense='min')

# Setting values for the rows (set the Left hand side constraints)
set.row(lprec_dummy, 1, c(1, 1, 1, 1), indices = c(1, 2, 3, 4))
set.row(lprec_dummy, 2, c(1, 1, 1, 1), indices = c(5, 6, 7, 8))
set.row(lprec_dummy, 3, c(1, 1), indices = c(1, 5))
set.row(lprec_dummy, 4, c(1, 1), indices = c(2, 6))
set.row(lprec_dummy, 5, c(1, 1), indices = c(3, 7))
set.row(lprec_dummy, 6, c(1, 1), indices = c(4, 8))

# Setting the right hand side values

rhs <- c(100, 120, 80, 60, 70, 10)
set.rhs(lprec_dummy, rhs)

# Setting constraint type and set variable types and bound

set.constr.type(lprec_dummy, c("=", "=", "=", "=", "=", "="))
set.bounds(lprec_dummy, lower = rep(0, 8))

# setting the decision variables (column) and constraints (rows)names

lp.rownames <- c("CapacityA", "CapacityB", "DemandW1", "DemandW2", "DemandW3", "DemandW4")
lp.colnames <- c("PlantAW1", "PlantAW2", "PlantAW3", "PlanntAW4", "PlantBW1", "PlantBW2", "PlantBW3", "PlantBW4")
dimnames(lprec_dummy) <- list(lp.rownames, lp.colnames)

# View the linear program object to make sure it's correct

lprec_dummy

# solving the model

solve(lprec_dummy)

# Show the value of objective function, variables, constraints


get.objective(lprec_dummy)
get.variables(lprec_dummy)
get.constraints(lprec_dummy)
get.constraints(lprec_dummy) - rhs


#saving into lp file
write.lp(lprec_dummy, filename = "AED_dummySOlution.lp", type = "lp")


# Read from file and solve it

x <- read.lp("AED_dummySOlution.lp")     # create an lp object x
x                          # display x
solve(x)                   # Solution
get.objective(x)           # get objective value
get.variables(x)           # get values of decision variables
get.constraints(x)         # get constraints

```
**Observations:**


1. We were **successfully able to solve** the LP problem using dummy variables.

2.The  minimized combined cost of production and shipping is  **132790**.

3.The AED should be produced for each plant based on each of the 4 warehouses are 0,60,40,80,0,30,0,10 for Plant1 warehouse 1,Plant1 warehouse 2,Plant 1 warehouse 3,Plant 1 warehouse 4,Plant 2 warehouse 1, Plant2 warehouse 2,Plant2 warehouse 3  ,Plant 2 warehouse 4 respectively.

4.Therefore,we can say that the **minimized cost is same using dummy variable approach and inequalities approach**.


--------------------------------------------------------------------------------------------------------------------



**Question 2:**

**Oil Distribution Texxon Oil Distributors, Inc., has three active oil wells in a west Texas
oil field. Well 1 has a capacity of 93 thousand barrels per day (TBD), Well 2 can produce
88 TBD, and Well 3 can produce 95 TBD. The company has five refineries along the
Gulf Coast, all of which have been operating at stable demand levels. In addition, three
pump stations have been built to move the oil along the pipelines from the wells to the
refineries. Oil can flow from any one of the wells to any of the pump stations, and from
any one of the pump stations to any of the refineries, and Texxon is looking for a
minimum cost schedule. The refineries’ requirements are as follows.**

**1) What is the minimum cost of providing oil to the refineries? Which wells are used
to capacity in the optimal schedule? Formulation of the problem is enough.**






**Solution:**

The transshipment model is an extension of the transportation model in which intermediate transshipment points are added between the sources and destinations.Therefore ,It seems Texxon Oil distrbuters problem would need to follow  an **Transshipment model approach**.


Formulation of the above problem seems to be **similiar to the standard Transportation problem (special type of LPP) but it has two phases**. Firstly oil moves from **three wells to any of the three pumps(Transshipment point)**, second phase is movement of oil **from three pumps to any of the five Refineries**.


Therefore, we need to determine out how much quantity of oil **from which well -> refinery -> which pump station** should be moved so that the total cost of these movements is minimum subject to availability and requirement constraints mentioned above.



Based on the daily cost given in the table  in dollars per thousand barrels and considering the company's cost accounting system recognized charges by the segment of pipeline that is used, we can determine the mimimum cost of providing oil to refineries with below formulation:

+ **Objective:**

**Minimize total cost** 

= 1.52X14 + 1.6X15 + 1.4X16 + 1.7X24 + 1.63X25 + 1.55X26 + 1.45X34 + 1.57X35 + 1.3X36 +
5.15X47 + 5.69X48 + 6.13X49 + 5.63X410 + 5.8X411 + 5.12X57 + 5.47X58 + 6.05X59 + 6.12X510 + 5.71X511 +
5.32X67 + 6.16X68 + 6.25X69 + 6.17X610 + 5.87X611


+ **subject to** :

X14 + X15 + X16 <=93 (Supply at Well 1)

X24 + X25 + X26 <=88 (Supply at Well 2)

X34 + X35 + X36 <=95 (Supply at Well 3)

X47 + X57 + X67 = 30 (Demand at Refinery 1)

X48 + X58 + X68 = 57 (Demand at Refinery 2)

X49 + X59 + X69 = 48 (Demand at Refinery 3)

X4,10 + X5,10 + X6, 10 = 91 (Demand at Refinery 4)

X4, 11 + X5, 11 + X6, 11 = 48 (Demand at Refinery 5)
)
X14+ X24+ X34= X47+ X48+ X49+ X410+ X411 (Shipping through Pump 1)

X15 + X25 + X35 = X57 + X58 + X59 + X510 + X511 (Shipping through Pump 2)

X16 + X26 + X36 = X67 + X68 + X69 + X610 + X611 (Shipping through Pump 3)

Xij ≥ 0 for all i and j (Non negativity constraint)


Now, in order to determine the which well will be used at its capacity , we need to solve the LP problem formulated above:

```{r}

#loading manually created LP file based on the above formulation

Oil_D <- read.lp("C:/Users/khush/Documents/Oil_distribution.lp")     # create an lp object x
Oil_D                          # display x
solve(Oil_D)                   # Solution
get.objective(Oil_D)           # get objective value
get.variables(Oil_D)           # get values of decision variables
get.constraints(Oil_D)         # get constraints

```
 

**Observation:**

Based on the above solution , we can see  that **Well 1 and Well 3** will be used at its maximum capacity.(values: 93 and 95 respectively for Well 1 and Well 3).
Well 2 is using only 86 from 88 capacity.



---

**2) Show the network diagram corresponding to the solution in (a). That is, label each
of the arcs in the solution and verify that the flows are consistent with the given
information.** 


Pump stations(Transshipment Points) and the number of units shipped from each  stations to each final destination (refinery plants), as these are the decisions management must make.
Assuming  the decision variables as number of units shipped from location (node) i to location (node) j
we get,

i = 1, 2, 3, 4, 5, 6

j = 4, 5, 6, 7, 8, 9, 10, 11


In the below figure  we can see nodes as the numbers and assigned one variable for each arc:

```{r}
#  install.packages("BiocManager")
#  BiocManager::install("EBImage")

library("EBImage")

#f = system.file("images", "abc.PNG", package="EBImage")
img = readImage("C:/Users/khush/Documents/images/Question2_Network_Daigram_v1.PNG")
img2 = readImage("C:/Users/khush/Documents/images/Question2_Network_Daigram_final.PNG")



display(img)
display(img2)


```
 
 
 Based on the second  network Diagram we can see derivation of below equations( constraints):
 
 
 
+ **Supply at Well**
 
X14 + X15 + X16 ≤ 93 (Supply at Well 1 **[node 1]**)

X24 + X25 + X26 ≤ 88 (Supply at Well 2 **[node 2]**)

X34 + X35 + X36 ≤ 95 (Supply at Well 3 **[node 3]**)

+ **Demand at Refinery**

X47 + X57 + X67 = 30 (Demand at Refinery 1 **[node 7]**)

X48 + X58 + X68 = 57 (Demand at Refinery 2 **[node 8]**)

X49 + X59 + X69 = 48 (Demand at Refinery 3 **[node 9]**)

X4,10 + X5,10 + X6, 10 = 91 (Demand at Refinery 4 **[node 10]**)

X4, 11 + X5, 11 + X6, 11 = 48 (Demand at Refinery 5 **[node 11]**)

+ **Shipping through Pump stations**

X14+ X24+ X34= X47+ X48+ X49+ X4,10+ X4,11 (Shipping through Pump 1 **[node 4]**)

X15 + X25 + X35 = X57 + X58 + X59 + X5,10 + X5,11 (Shipping through Pump 2 **[node 5]**)

X16 + X26 + X36 = X67 + X68 + X69 + X6,10 + X6,11 (Shipping through Pump 3 ***[node 6]**)

Xij ≥ 0 for all i and j (Non negativity constraint)







------------------------------------------------------------------------------------------------------------
------------------------------------------------------------------------------------------------------------